Maximum Entropy Spectral Analysis: a case study

### 2021-03-25 paper/mesa.tex
Edit in caption welch comparison

\begin{figure}
	\caption{Make here a comparison between Welch - Fake data}
	\label{fig:mem_welch_fakedata}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_True.pdf}
\end{figure}

\begin{figure}
	\caption{Make here a comparison between Welch - True data}
	\label{fig:mem_welch_realdata}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_False.pdf}
\end{figure}

@@

Looking at the low frequencies, it is striking to note that FPE does not capture the peak $f_{yr} = \SI{1}{yr^{-1}}$ located at the frequency of a year. On the other hand, the peak is captured well by the CAT loss function.
In analogy as what observed for the peak at $f_D$, in the CAT spectru we observe a higher order harmonic at a frequency $2 \cdot f_{yr}$. As in the previous case, this is required to better model the temperature variation in the year.

>>>>

\begin{figure}
	\caption{Comparison between PSD estimation with Welch method (blue) and Maximum Entropy (red) for \textit{synthetic} LIGO data. The estimation is based data with an increasing observation time $T = 1, 5, 10, 100, \SI{1000}{s}$. In dashed black is reported the true PSD (from which data are generated).}
	\label{fig:mem_welch_fakedata}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_True.pdf}
\end{figure}

\begin{figure}
	\caption{Comparison between PSD estimation with Welch method (blue) and Maximum Entropy (red) for \textit{real} LIGO data. The estimation is based data with an increasing observation time $T = 1, 5, 10, 100, \SI{1000}{s}$.}
	\label{fig:mem_welch_realdata}
	\includegraphics{Images/comparison_LVC_data/comparison_LVC_data_overall_fake_False.pdf}
\end{figure}

@@

Looking at the low frequencies, it is striking to note that FPE does not capture the peak $f_{yr} = \SI{1}{yr^{-1}}$ located at the frequency of a year. On the other hand, the peak is captured well by the CAT loss function.
In analogy as what observed for the peak at $f_D$, in the CAT spectrum we observe a higher order harmonic at a frequency $2 \cdot f_{yr}$. As in the previous case, this is required to better model the temperature variation in the year.
